---
title: "train-test"
author: "Nisha Doshi"
date: "2025-03-31"
output: html_document
---

```{r}
fitness_data <- read.csv("health_fitness_dataset.csv")

fitness_data$health_condition <- factor(fitness_data$health_condition)
fitness_data$health_condition <- relevel( fitness_data$health_condition, ref = "None" )


fitness_data$smoking_status <- factor(fitness_data$smoking_status)
fitness_data$smoking_status<- relevel( fitness_data$smoking_status, ref = "Never" )

fitness_data$intensity <- factor(fitness_data$intensity)
fitness_data$intensity <- relevel(fitness_data$intensity, ref = "Low" )

```

```{r}
library(caTools)
library(tidyverse)

fitness_data_mod <- dplyr::select(fitness_data, -weight_kg, -fitness_level, -date)

fitness_data_mod$weight_kg <- fitness_data_mod$bmi * (fitness_data_mod$height_cm/100)^2

numeric_vars <- c("age", "height_cm", "duration_minutes", "avg_heart_rate", 
                  "hours_sleep", "stress_level", "daily_steps", 
                  "hydration_level", "bmi", "resting_heart_rate", 
                  "blood_pressure_systolic", "blood_pressure_diastolic", "weight_kg")

fitness_data_test <- dplyr::select(fitness_data, -weight_kg, -fitness_level, -date)

fitness_data_test$weight_kg <- fitness_data_test$bmi * (fitness_data_test$height_cm/100)^2

# Scale only predictor variables (center = TRUE, scale = TRUE)
fitness_data_mod[, numeric_vars] <- scale(fitness_data_mod[, numeric_vars])


set.seed(123)

# Stratified sampling based on activity_type
split <- sample.split(fitness_data_mod$activity_type, SplitRatio = 0.8)

# Subset data into training and testing sets
train_data <- subset(fitness_data_mod, split == TRUE)
test_data <- subset(fitness_data_mod, split == FALSE)


```


```{r}
set.seed(123)


features_for_clustering <- train_data %>% 
  dplyr::select(age, weight_kg)  

sampled_data <- features_for_clustering %>% sample_n(10000)  # adjust n depending on your RAM

fviz_nbclust(sampled_data, kmeans, method = "wss")

```


```{r}
library(dplyr)

features_for_clustering <- train_data %>% 
  dplyr::select(age, weight_kg)  

# KMeans on multivariate data
set.seed(123)
k_clusters <- kmeans(features_for_clustering, centers = 8)

# Add cluster info to your train data
train_data$multi_cluster <- as.factor(k_clusters$cluster)

library(ggplot2)

# Run PCA for visualization
pca_result <- prcomp(features_for_clustering, scale. = TRUE)

# Create a data frame for plotting
pca_df <- as.data.frame(pca_result$x[, 1:2])  # First two principal components
pca_df$cluster <- train_data$multi_cluster

# Plot with ggplot2
ggplot(pca_df, aes(x = PC1, y = PC2, color = cluster)) +
  geom_point(alpha = 0.7, size = 3) +
  labs(title = "KMeans Clustering (PCA-reduced)", x = "PC1", y = "PC2") +
  theme_minimal()


```

This is all 1st attempt clustering code...
library(dplyr)

features_for_clustering <- train_data %>% 
  dplyr::select(age, duration_minutes, avg_heart_rate, weight_kg, daily_steps)  

# KMeans on multivariate data
set.seed(123)
k_clusters <- kmeans(features_for_clustering, centers = 8)

# Add cluster info to your train data
train_data$multi_cluster <- as.factor(k_clusters$cluster)

library(ggplot2)

# Run PCA for visualization
pca_result <- prcomp(features_for_clustering, scale. = TRUE)

# Create a data frame for plotting
pca_df <- as.data.frame(pca_result$x[, 1:2])  # First two principal components
pca_df$cluster <- train_data$multi_cluster

# Plot with ggplot2
ggplot(pca_df, aes(x = PC1, y = PC2, color = cluster)) +
  geom_point(alpha = 0.7, size = 3) +
  labs(title = "KMeans Clustering (PCA-reduced)", x = "PC1", y = "PC2") +
  theme_minimal()


UNSCALING AND CLUSTER ANALYSIS
```{r}
library(dplyr)

activity_v_cluster <- train_data %>% 
  group_by(activity_type, multi_cluster) %>%
  summarise(count = n()) %>%
  tidyr::pivot_wider(names_from = multi_cluster, values_from = count, values_fill = 0)



# Convert to long format
long_data <- activity_v_cluster %>%
  pivot_longer(cols = -activity_type, names_to = "Cluster", values_to = "Count")

ggplot(long_data, aes(x = Cluster, y = Count, fill = Cluster)) +
  geom_bar(stat = "identity") +
  facet_wrap(~activity_type, scales = "free_y") +  # one plot per activity
  labs(title = "Cluster Distribution by Activity",
       x = "Cluster",
       y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")  # Optional: remove legend since clusters are on x-axis



cluster_summary <- train_data %>%
  group_by(multi_cluster) %>%
  summarise(
    avg_age = round(mean(age, na.rm = TRUE), 1),
    avg_weight = round(mean(weight_kg, na.rm = TRUE), 1),

  )


age_center <- mean(fitness_data$age)
age_scale <- sd(fitness_data$age)


weight_center <- mean(fitness_data$weight_kg)
weight_scale <- sd(fitness_data$weight_kg)



cluster_summary_unscaled <- cluster_summary %>%
  mutate(
    unscaled_avg_age = (avg_age * age_scale) + age_center,
    unscaled_avg_weight = (avg_weight * weight_scale) + weight_center,
  )

```


Lets see the health distribution among clusters
This was to see whether or no health conditions should be considered in clustering 
The disribution is fairly even throughout with some differences so I am going to use health conditions for filtering 

“While health_condition was not included as a clustering variable, I analyzed its distribution across clusters post hoc. This allowed me to assess whether the clusters incidentally captured health-related patterns. The relatively even distribution of conditions such as asthma, diabetes, and hypertension suggests that clustering based on behavioral and physiological features (e.g., age, weight, heart rate) still provides useful groupings. To ensure realistic and safe recommendations, I incorporate health_condition as a filtering layer when generating activity suggestions.”
```{r}
cluster_1_data <- subset(train_data, multi_cluster == 1)
cluster_2_data <- subset(train_data,multi_cluster ==2)
cluster_3_data <- subset(train_data, multi_cluster ==3)
cluster_4_data <- subset(train_data, multi_cluster == 4)
cluster_5_data <- subset(train_data, multi_cluster == 5)
cluster_6_data <- subset(train_data, multi_cluster ==6)
cluster_7_data <-subset(train_data, multi_cluster ==7)
cluster_8_data <-subset(train_data, multi_cluster ==8)

table(cluster_1_data$health_condition)
table(cluster_2_data$health_condition)
table(cluster_3_data$health_condition)
table(cluster_4_data$health_condition)
table(cluster_5_data$health_condition)
table(cluster_6_data$health_condition)
table(cluster_7_data$health_condition)
table(cluster_8_data$health_condition)

health_cluster_counts <- train_data %>%
  group_by(multi_cluster, health_condition) %>%
  summarise(count = n(), .groups = 'drop')

# Option 1: Stacked bar plot (raw counts)
ggplot(health_cluster_counts, aes(x = multi_cluster, y = count, fill = health_condition)) +
  geom_bar(stat = "identity") +
  labs(title = "Health Conditions by Cluster", x = "Cluster", y = "Count") +
  theme_minimal()

```
```{r}
table(cluster_1_data$smoking_status)
table(cluster_2_data$smoking_status)
table(cluster_3_data$smoking_status)
table(cluster_4_data$smoking_status)
table(cluster_5_data$smoking_status)
table(cluster_6_data$smoking_status)
table(cluster_7_data$smoking_status)
table(cluster_8_data$smoking_status)

health_cluster_counts <- train_data %>%
  group_by(multi_cluster, smoking_status) %>%
  summarise(count = n(), .groups = 'drop')

# Option 1: Stacked bar plot (raw counts)
ggplot(health_cluster_counts, aes(x = multi_cluster, y = count, fill = smoking_status)) +
  geom_bar(stat = "identity") +
  labs(title = "Smoking Status by Cluster", x = "Cluster", y = "Count") +
  theme_minimal()

```



```{r}
## create 10 groups splits on activity type
groups <- split(train_data, train_data$activity_type)

basketball <- groups[[1]]
cycling <- groups[[2]]
dancing <- groups[[3]]
hiit <- groups[[4]]
running <- groups[[5]]
swimming <- groups[[6]]
tennis <- groups[[7]]
walking <- groups[[8]]
weight_training <- groups[[9]]
yoga <- groups[[10]]


```


```{r}

##dont use
cluster_scaled_means <- train_data %>%
  group_by(multi_cluster) %>%
  summarise(
    avg_age = mean(age),
    avg_duration = mean(duration_minutes),
    avg_heart_rate = mean(avg_heart_rate),
    avg_weight = mean(weight_kg),
    avg_steps = mean(daily_steps),
    avg_sleep = mean(hours_sleep),
    .groups = "drop"
  )

print(cluster_scaled_means)
```



```{r}
##dont use
library(dplyr)

cluster_summary <- train_data_unscaled %>%
  group_by(multi_cluster) %>%
  summarise(
    count = n(),
    avg_age = round(mean(age_unscaled), 1),
    avg_duration = round(mean(duration_minutes_unscaled), 1),
    avg_heart_rate = round(mean(avg_heart_rate_unscaled), 1),
    avg_weight = round(mean(weight_kg_unscaled), 1),
    avg_steps = round(mean(daily_steps_unscaled), 0),
    avg_sleep = round(mean(hours_sleep_unscaled), 1)
  )

```


```{r}
library(dplyr)

# Ensure groups list has names
names(groups) <- unique(train_data$activity_type)

# Create an empty list to store the summarized data frames
condensed_groups <- list()

# Loop through each activity type
for (activity in names(groups)) {
  condensed_groups[[activity]] <- groups[[activity]] %>%
    group_by(participant_id) %>%
    summarise(
      age = first(age),
      gender = first(gender),
      height_cm = first(height_cm),
      resting_heart_rate = first(resting_heart_rate),
      blood_pressure_diastolic = first(blood_pressure_diastolic),
      blood_pressure_systolic = first(blood_pressure_systolic),
      health_condition = first(health_condition),
      smoking_status = first(smoking_status),
      bmi = first(bmi),
      weight_kg = first(weight_kg),
      
      duration_minutes = mean(duration_minutes, na.rm = TRUE),
      calories_burned = mean(calories_burned, na.rm = TRUE),
      avg_heart_rate = mean(avg_heart_rate, na.rm = TRUE),
      hours_sleep = mean(hours_sleep, na.rm = TRUE),
      stress_level = mean(stress_level, na.rm = TRUE),
      daily_steps = mean(daily_steps, na.rm = TRUE),
      hydration_level = mean(hydration_level, na.rm = TRUE), 
      
      intensity = names(sort(table(intensity), decreasing = TRUE)[1]),
      multi_cluster = names(sort(table(multi_cluster), decreasing = TRUE)[1])
    )
}

# Assign each summarized dataset as a separate variable
list2env(condensed_groups, envir = .GlobalEnv)


```

Now that I have my clusters, I am going to split each activity data set by cluster 
```{r}
split_data <- list()

# Loop over each activity and split by cluster
for (activity in names(condensed_groups)) {
  df <- condensed_groups[[activity]]
  
  for (cluster in unique(df$multi_cluster)) {
    cluster_df <- df[df$multi_cluster == cluster, ]
    
    # Drop columns you don’t want in your modeling
    cluster_df <- cluster_df %>%
      dplyr::select(-multi_cluster, -participant_id, -bmi)  # adjust this list if needed
    
    # Save it in a nested list structure
    split_data[[paste(activity, cluster, sep = "_Cluster")]] <- cluster_df
  }
}

```

TESTING 1MODEL
Running step wise to see if there is a maximal model w the lowest AIC
However, turns out the full model is the best model, it has the lowest AIC and each time a predictor gets removed the AIC significantly increases. 

Also the VIF will tell me if age or avg heart rate needs to be removed, neight do! low enough numbers to not be considered for multicollinearity. In some models age and avg heart rate show significant and in other only age or only avg heart rate show up significant 
```{r}
example <- lm(calories_burned ~ . , data = split_data[["HIIT_Cluster4"]])
example1 <- lm(calories_burned ~ . , data = split_data[["HIIT_Cluster4"]])
example2 <- lm(sqrt(calories_burned) ~. -avg_heart_rate , data = split_data[["HIIT_Cluster4"]])
summary(example)
summary(example1)
summary(example2)

vif(example)

par(mfrow = c(2, 2))
plot(example)

require(MASS)
boxcox(example)

par(mfrow = c(2, 2))
plot(example1)

par(mfrow = c(2, 2))
plot(example2)
```

BOXCOX= 0.5 indiciating to use square root, however noticing that srt is decreasing the R^2


```{r}
# Fit a model on one of the sets

model <- lm(sqrt(calories_burned) ~ . , data = split_data[["Dancing_Cluster4"]])
summary(model)
model1 <- lm(sqrt(calories_burned) ~ . , data = split_data[["HIIT_Cluster4"]])
model2 <- lm(sqrt(calories_burned) ~ . , data = split_data[["Walking_Cluster4"]])
test_user <- condensed_test_data %>% 
  filter(participant_id == 1)

pred1 <- predict(model, newdata = test_user)
pred2 <- predict(model1, newdata = test_user)
pred3 <- predict(model2, newdata = test_user)
pred1^2
pred2^2
pred3^2

require(MASS)
max_model = lm(sqrt(calories_burned) ~ . , data = split_data[["HIIT_Cluster4"]])
best_model = step(max_model, direction = "backward")


library(car)
vif(model)

```

now lets run it across all activities and clusters

```{r}
# Initialize a list to store models
models <- list()

# Loop through each dataset in split_data
for (dataset_name in names(split_data)) {
  # Fit the linear model on the dataset
  model <- lm(sqrt(calories_burned) ~ . -avg_heart_rate, data = split_data[[dataset_name]])
  
  # Store the model in the list
  models[[dataset_name]] <- model
  
  # Print the summary of the model (optional, to check the results)
  print(paste("Model for", dataset_name))
  print(summary(model))
}

```
ANALYSIS (PLOTS ETC ETC ETC) 
```{r}

```




OK NOW TESTINGGGG

Using Eucilidean distance for test clustering. 
```{r}
test_features <- test_data %>% 
  dplyr::select(age, weight_kg)

assign_clusters <- function(new_data, centers) {
  apply(new_data, 1, function(row) {
    dists <- apply(centers, 1, function(center) sum((row - center)^2))
    which.min(dists)
  })
}

# Assign clusters to test data
test_data$multi_cluster <- as.factor(assign_clusters(test_features, k_clusters$centers))


```


```{r}
# Condense the test set by participant_id
condensed_test_data <- test_data %>%
  group_by(participant_id) %>%
  summarise(
    age = first(age),
    gender = first(gender),
    height_cm = first(height_cm),
    resting_heart_rate = first(resting_heart_rate),
    blood_pressure_diastolic = first(blood_pressure_diastolic),
    blood_pressure_systolic = first(blood_pressure_systolic),
    health_condition = first(health_condition),
    smoking_status = first(smoking_status),
    bmi = first(bmi),
    weight_kg = first(weight_kg),
    
    duration_minutes = mean(duration_minutes, na.rm = TRUE),
    calories_burned = mean(calories_burned, na.rm = TRUE),
    avg_heart_rate = mean(avg_heart_rate, na.rm = TRUE),
    hours_sleep = mean(hours_sleep, na.rm = TRUE),
    stress_level = mean(stress_level, na.rm = TRUE),
    daily_steps = mean(daily_steps, na.rm = TRUE),
    hydration_level = mean(hydration_level, na.rm = TRUE), 
    
    intensity = names(sort(table(intensity), decreasing = TRUE)[1]),
      multi_cluster = names(sort(table(multi_cluster), decreasing = TRUE)[1]),
    
    # Assign the most frequent activity type for each participant
    activity_type = names(sort(table(activity_type), decreasing = TRUE)[1])
  )
```

```{r}
set.seed(42)
sampled_test_users <- test_data %>%
  group_by(multi_cluster) %>%
  slice_sample(n = 1)


# Initialize an empty list to hold models by cluster
cluster_models <- list()

# Loop over each model name in the models list
for (model_name in names(models)) {
  # Split the model name (e.g., "Dancing_Cluster4") into parts
  name_parts <- strsplit(model_name, "_")[[1]]
  cluster_number <- name_parts[2]  # e.g., "Cluster4"
  
  # Initialize list for this cluster if it doesn't exist
  if (!(cluster_number %in% names(cluster_models))) {
    cluster_models[[cluster_number]] <- list()
  }
  
  # Add the model to the corresponding cluster group
  cluster_models[[cluster_number]][[model_name]] <- models[[model_name]]
}

# Done!
print(names(cluster_models))

```



CLUSTER 4 
```{r}
# Filter the test user
test_user <- condensed_test_data %>% 
  filter(participant_id == 1)

# Get models for Cluster 4
models_cluster4 <- cluster_models[["Cluster4"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 4
for (model_name in names(models_cluster4)) {
  model <- models_cluster4[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)

```

CLUSTER 1
```{r}
## 614 
## 775
test_user <- condensed_test_data %>% 
  filter(participant_id == 614)

# Get models for Cluster 4
models_cluster1 <- cluster_models[["Cluster1"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 4
for (model_name in names(models_cluster1)) {
  model <- models_cluster1[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)

```

ClUSTER 2 
```{r}
test_user <- condensed_test_data %>% 
  filter(participant_id == 336)

# Get models for Cluster 4
models_cluster4 <- cluster_models[["Cluster2"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 4
for (model_name in names(models_cluster4)) {
  model <- models_cluster4[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)
```


CLUSTER 3
```{r}
##916
test_user <- condensed_test_data %>% 
  filter(participant_id == 3)

# Get models for Cluster 3
models_cluster3 <- cluster_models[["Cluster3"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 3
for (model_name in names(models_cluster3)) {
  model <- models_cluster3[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)
```
CLUSTER 4
```{r}
##1373
test_user <- condensed_test_data %>% 
  filter(participant_id == 1373)

# Get models for Cluster 3
models_cluster4 <- cluster_models[["Cluster4"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 4
for (model_name in names(models_cluster4)) {
  model <- models_cluster4[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)
```
view(fitness_data_test %>% filter(participant_id == 916))
view(condensed_test_data %>% filter(multi_cluster==4))

CLUSTER 5
```{r}
##637
test_user <- condensed_test_data %>% 
  filter(participant_id == 637)

# Get models for Cluster 3
models_cluster5 <- cluster_models[["Cluster5"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 5
for (model_name in names(models_cluster5)) {
  model <- models_cluster5[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)
```
CLUSTER 6
```{r}
##637
test_user <- condensed_test_data %>% 
  filter(participant_id == 1350)

# Get models for Cluster 6
models_cluster6 <- cluster_models[["Cluster6"]]

# Initialize a list to store predictions
predictions <- list()

# Loop through each model in Cluster 6
for (model_name in names(models_cluster6)) {
  model <- models_cluster6[[model_name]]
  
  # Predict
  pred <- predict(model, newdata = test_user)
  
  # Square it (since you used sqrt in training)
  pred_squared <- pred^2
  
  # Store in list with model name
  predictions[[model_name]] <- pred_squared
}

# View predictions
print(predictions)
```


PREVIOUS WORK 
```{r}
models <- list()

# Loop through each summarized dataset
for (activity in names(condensed_groups)) {
  df <- condensed_groups[[activity]]
  
  # Check if there are enough rows for regression
  if (nrow(df) > 1) {  
    models[[activity]] <- lm(sqrt(calories_burned) ~ . -participant_id -bmi -avg_heart_rate, data = df)
  } else {
    models[[activity]] <- NULL  # Skip if not enough data
  }
}

for (activity in names(models)) {
    cat("### Summary for Activity:", activity, "###\n")
    print(summary(models[[activity]]))
  }


ggplot(condensed_mod, aes(x = health_condition, y = calories_burned, fill = health_condition)) +
  geom_boxplot() +
  labs(title = "Calories Burned Across Health Conditions", x = "Health Condition", y = "Calories") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot(condensed_mod$weight_kg, condensed_mod$calories_burned)

library(ggplot2)

ggplot(condensed_mod, aes(x = weight_kg, y = calories_burned)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) + # Add points
  geom_smooth(method = "lm", se = FALSE, color = "orange") + # Add a linear regression line
  labs(
    title = "Calories Burned vs. Weight",
    x = "Weight (kg)",
    y = "Calories Burned"
  ) +
  theme_minimal() + # Use a clean theme
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"), # Center title and make it bold
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )


# 1. Histogram of Duration
# 2. Density Plot of Duration
ggplot(condensed_mod, aes(x = duration_minutes)) +
  geom_density(fill = "lightgreen", alpha = 0.7) +
  labs(
    title = "Density Plot of Activity Durations",
    x = "Duration (minutes)",
    y = "Density"
  ) +
  theme_minimal()


```

```{r}
# Extract coefficients from each model into a dataframe
coef_table <- do.call(cbind, lapply(models, function(mod) coef(summary(mod))[, "Estimate"])) 

# Convert to data frame and give row names
coef_table <- as.data.frame(coef_table)
rownames(coef_table) <- names(coef(models[[1]]))  # Set variable names as row names

```

```{r}
library(ggplot2)
library(reshape2) # To reshape data

coef_table$Predictor <- rownames(coef_table)
# Convert to long format
coef_long <- melt(coef_table, id.vars = "Predictor", variable.name = "Activity", value.name = "Coefficient")

# Exclude a specific predictor (e.g., "bmi")
coef_long_filtered <- coef_long %>% filter(Predictor != "(Intercept)")

# Plot without "bmi"
ggplot(coef_long_filtered, aes(x = Activity, y = Coefficient, color = Predictor)) +
  geom_point() +
  theme_minimal() +
  coord_flip() +
  labs(title = "Comparison of Coefficients Across Activities")
```

```{r}
# Filter for only "duration_minutes"
coef_duration <- coef_long %>% filter(Predictor == "duration_minutes")

# Plot duration_minutes coefficients across activities
ggplot(coef_duration, aes(x = Activity, y = Coefficient)) +
  geom_col(fill = "steelblue") +  # Use bars instead of points for better comparison
  theme_minimal() +
  coord_flip() +  # Flip for better readability
  labs(title = "Effect of Duration (minutes) Across Activities",
       y = "Coefficient Value",
       x = "Activity Type")
```

```{r}
# Filter for only "daily_steps"
coef_steps <- coef_long %>% filter(Predictor == "daily_steps")

# Plot daily steps coefficients across activities
ggplot(coef_steps, aes(x = Activity, y = Coefficient)) +
  geom_col(fill = "steelblue") +  # Use bars instead of points for better comparison
  theme_minimal() +
  coord_flip() +  # Flip for better readability
  labs(title = "Effect of Daily Steps Across Activities",
       y = "Coefficient Value",
       x = "Activity Type")
```



```{r}
fitness_data_mod1 <- dplyr::select(fitness_data, -weight_kg, -fitness_level, -date)

fitness_data_mod1$weight_kg <- fitness_data_mod1$bmi * (fitness_data_mod1$height_cm/100)^2

condensed_mod <- fitness_data_mod1 %>%
  group_by(participant_id) %>%
  summarise(
    age = first(age),
    gender = first(gender),
    height_cm = first(height_cm),
    resting_heart_rate = first(resting_heart_rate),
    blood_pressure_diastolic = first(blood_pressure_diastolic),
    blood_pressure_systolic = first(blood_pressure_systolic),
    health_condition = first(health_condition),
    smoking_status = first(smoking_status),
    bmi = first(bmi),
    weight_kg = first(weight_kg),
    
    duration_minutes = mean(duration_minutes, na.rm = TRUE),
    calories_burned = mean(calories_burned, na.rm = TRUE),
    avg_heart_rate = mean(avg_heart_rate, na.rm = TRUE),
    hours_sleep = mean(hours_sleep, na.rm = TRUE),
    stress_level = mean(stress_level, na.rm = TRUE),
    daily_steps = mean(daily_steps, na.rm = TRUE),
    hydration_level = mean(hydration_level, na.rm = TRUE), 
    
    intensity = names(sort(table(intensity), decreasing = TRUE)[1]),
    
    # Assign the most frequent activity type for each participant
    activity_type = names(sort(table(activity_type), decreasing = TRUE)[1])
  )
```


